The K2 Bright Star Survey I: Methodology and Data Release

### 2019-07-03 paper/ms.tex
cheops
deathstar section filled in

In addition to expanding the range of possible objective functions, we have also added a feature `\texttt{deathstar}' to deal with contamination. We apply the watershed-based image segmentation algorithm from \textsc{k2p2} \citep{k2p2} to the input target pixel file datacube to identify possible background sources and cut them out. \textcolor{red}{More here from Tim.} Other than this, we have adopted less-aggressive quality flagging, having found that many cadences were being classified as bad quality for spurious `cosmic ray' events, which were actually caused by a combination of saturation and spacecraft motion. We instead chose to iteratively sigma-clip outliers and retain cadences with the \texttt{lightkurve} default quality mask.

@@

We have detected two eclipsing binaries in our sample: the previously-known EB HR\,6773 and the new detection 98\,Tau.

@@

% interesting EB - 98 Tau
The chemically-peculiar A0V star 98\,Tau is of special interest for studies of surface inhomogeneity. We detected variability with a fundamental period of 1.74~d with twice as much power at the first harmonic ($P = 0.87$\,d), which is consistent with $\alpha^2$\,CVn spot modulation from a rapidly-rotating star. This star also experiences a transit of depth 0.03, which for a 1.87\,\rsun typical A0V star implies an 0.3\,\rsun stellar mass companion. With rotational modulation and an eclipse to break degeneracies, models such as \texttt{starry} \citep{starry} can infer surface brightness maps and reveal the spatial distribution of the star's chemical peculiarity.

>>>>

In addition to expanding the range of possible objective functions, we have also added a feature `\texttt{deathstar}' to deal with contamination. Clusters of pixels are identified with the DBSCAN algorithm \citep[Density-based spatial clustering of applications with noise;][]{dbscan}, and we join these clusters with the watershed-based image segmentation algorithm from \textsc{k2p2} \citep{k2p2}. Clusters other than the target star identified by this algorithm are identified as possible background sources and removed from the target pixel file before processing. Other than this, we have adopted less-aggressive quality flagging, having found that many cadences were being classified as bad quality for spurious `cosmic ray' events, which were actually caused by a combination of saturation and spacecraft motion. We instead chose to iteratively sigma-clip outliers and retain cadences with the \texttt{lightkurve} default quality mask.

@@

We have detected two eclipsing binaries in our sample: the previously-known EB HR~6773 and the new detection 98~Tau. After subtracting an EB model for HR~6773, we find additional variability consistent with SPB pulsations.

@@

% interesting EB - 98 Tau
The chemically-peculiar A0V star 98~Tau is of special interest for studies of surface inhomogeneity. We detected variability with a fundamental period of 1.74~d with twice as much power at the first harmonic ($P = 0.87$\,d), which is consistent with $\alpha^2$\,CVn spot modulation from a rapidly-rotating star. This star also experiences a transit of depth 0.03, which for a 1.87\,\rsun typical A0V star implies an 0.3\,\rsun stellar mass companion.

These systems contain variable stars in the brightest EBs in \ktwo, and are therefore unique targets for follow-up with smaller telescopes. With an eclipse to break degeneracies, models such as \texttt{starry} \citep{starry} has been shown to robustly and uniquely infer surface brightness maps from light curves. High-time-cadence photometry during transit, such as with CHEOPS \citep{cheops}, will reveal the spatial distribution of the star's chemical peculiarity or pulsation.
